---
title: "Thesis Practice"
author: "Pepijn Vink"
date: "3/6/2022"
output: pdf_document
---
Packages
```{r}
library(BayesFactor)
library(tidyverse)
library(magrittr)
library(jtools)
library(bayestestR)
library(gmodels)
library(BRRR)
library(skimr)
library(tidybayes)
library(patchwork)
library(pwr)
```
Create column names
```{r}
col_names <- c("difference", "n", "mean1", "mean2", "sd", "y1", "y2", "diff_obs", "p", "ci.low","ci.high", "HDI.low", "HDI.high", "BayesFactor", "BFa", "p.decision", "BF1.decision", "BF3.decision", "BF10.decision", "BF30.decision", "BF.3.cor", "BF.10.cor", "BF.30.cor", "BF.3.ninc", "BF.10.ninc", "BF.30.ninc", "BF.evidence", "post.null", "post.alt", "HDI.decision", "CI.est.correct", "HDI.est.correct", "ci.width", "hdi.width")
```
Write function to make simulation more smooth. BF 'cutoffs' and evidence levels are based on Jeffrey's (1961). For p values, CI's and HDI's, 1 indicates rejection of the null and 0 no rejection. For the BF's at every cutoff value, 0 indicates preference for the null, 1 indicates no preference, and 2 indicates preference for the alternative/complement. Posterior probabilities are based on equal prior odds.

```{r}
freq.bayes <- function(sample.size = 10, iterations = 10, mean.low = 100, sd = 10, difference = 0, seed = NA){
col_names <- c("difference", "n", "mean1", "mean2", "sd", "y1", "y2", "diff_obs", "p", "ci.low","ci.high", "HDI.low", "HDI.high", "BayesFactor", "BFa", "p.decision", "BF1.decision", "BF3.decision", "BF10.decision", "BF30.decision", "BF.3.cor", "BF.10.cor", "BF.30.cor", "BF.3.ninc", "BF.10.ninc", "BF.30.ninc", "BF.evidence", "post.null", "post.alt", "HDI.decision", "CI.est.correct", "HDI.est.correct", "ci.width", "hdi.width")

save <- matrix(data = NA, nrow = iterations, ncol = 34)

set.seed(seed)
  for(i in 1:iterations){
    diff <- difference
    n <- sample.size
    
    mean2 <- mean.low
    mean1 <- mean2 + diff
    sd <- 10
    
    y1 <- rnorm(n = n, mean = mean1, sd = sd)
    y2 <- rnorm(n = n, mean = mean2, sd = sd)
    
    result <- t.test(y1, y2, var.equal = TRUE)
    p <- result$p.value
    ci <- result$conf.int
    
    mean_y1 <- mean(y1)
    mean_y2 <- mean(y2)
    
    ci.low <- ci[1]
    ci.high <- ci[2]
    
    mean_diff <- mean(y1) - mean(y2)
    
    bfa <- ttestBF(y1, y2)
    
    bf0 <- 1/bfa
    
    post <- bayestestR::hdi(bfa)
    
    HDI.low <- post$CI_low
    
    HDI.high <- post$CI_high
    
    BFa <- extractBF(bfa)$bf
    
    BF0 <- extractBF(bf0)$bf
    
    p_correct <- case_when(p < 0.05 ~ "alt",
                           TRUE ~ "null")
    
    BF.3 <- case_when(BF0 >= 3 ~ "null",
                      BF0 < 3 & BFa < 3 ~ "U",
                      BFa >= 3 ~ "alt")

    BF.10 <- case_when(BF0 >= 10 ~ "null",
                      BF0 < 10 & BFa < 10 ~ "U",
                      BFa >= 10 ~ "alt")
    
    BF.30 <- case_when(BF0 >= 30 ~ "null",
                      BF0 < 30 & BFa < 30 ~ "U",
                      BFa >= 30 ~ "alt")
    
    BF.1 <- case_when(BF0 > 1 ~ "null",
                              TRUE ~ "alt")
    
    BF.3.dich.cor <- case_when(BFa > 3 & diff != 0 ~ "correct",
                               BF0 > 3 & diff == 0 ~ "correct",
                               TRUE ~ "incorrect")
    BF.10.dich.cor <- case_when(BFa > 10 & diff != 0 ~ "correct",
                               BF0 > 10 & diff == 0 ~ "correct",
                               TRUE ~ "incorrect")
    
    BF.30.dich.cor <- case_when(BFa > 30 & diff != 0 ~ "correct",
                               BF0 > 30 & diff == 0 ~ "correct",
                               TRUE ~ "incorrect")
    
    BF.3.dich.nincor <- case_when(BF0 < 3 & diff != 0 ~ "correct",
                               BFa < 3 & diff == 0 ~ "correct",
                               TRUE ~ "incorrect")
    
    BF.10.dich.nincor <- case_when(BF0 < 10 & diff != 0 ~ "correct",
                               BFa < 10 & diff == 0 ~ "correct",
                               TRUE ~ "incorrect")
    
    BF.30.dich.nincor <- case_when(BF0 < 30 & diff != 0 ~ "correct",
                               BFa < 30 & diff == 0 ~ "correct",
                               TRUE ~ "incorrect")
    
    BF.evidence <- case_when(BF0 < 1/100 ~ -5,
                             BF0 >= 1/100 & BF0 < 1/30 ~ -4,
                             BF0 >= 1/30 & BF0 < 1/10 ~ -3,
                             BF0 >= 1/10 & BF0 < 1/3 ~ -2,
                             BF0 >= 1/3 & BF0 < 1 ~ -1,
                             BF0 == 1 ~ 0,
                             BF0 > 1 & BF0 <= 3 ~ 1,
                             BF0 > 3 & BF0 <= 10 ~ 2,
                             BF0 > 10 & BF0 <= 30 ~ 3,
                             BF0 > 30 & BF0 <= 100 ~ 4,
                             BF0 > 100 ~ 5)
    post.alt <- 1/(BF0+1)
    
    post.null <- 1/(BFa+1)
      
    HDI_decision <- case_when(HDI.low <= 0 & HDI.high >= 0 ~ "null",
                             TRUE ~ "alt")
    
    HDI_correct_est <- case_when(HDI.low <= diff & HDI.high >= diff ~ "correct",
                                 TRUE ~ "incorrect")
    
    CI_correct_est <- case_when(ci.low <= diff & ci.high >= diff ~ "correct",
                                 TRUE ~ "incorrect")
    
    HDI.width <- HDI.high - HDI.low
    
    CI.width <- ci.high - ci.low
    
    vec <- c(diff, n, mean1, mean2, sd, mean_y1, mean_y2, mean_diff, p, ci.low, ci.high, HDI.low, HDI.high, BF0, BFa, p_correct, BF.1, BF.3, BF.10, BF.30, BF.3.dich.cor, BF.10.dich.cor, BF.30.dich.cor, BF.3.dich.nincor, BF.10.dich.nincor, BF.30.dich.nincor, BF.evidence,  post.null, post.alt, HDI_decision, CI_correct_est, HDI_correct_est, CI.width, HDI.width)
    
    save[i,] <- vec
  }
colnames(save) <- col_names
save
}
```
# Simulate different sample sizes

## Power analysis to determine samle size for power of 50% and 80%
```{r}
pwr.t.test(d = 0.5, power = 0.5, type = "two.sample", alternative = "two.sided")
pwr.t.test(d = 0.5, power = 0.8, type = "two.sample", alternative = "two.sided")
```

## No effect
```{r}
# n = 10
df0.n10 <- as.data.frame(freq.bayes(sample.size = 10, iterations = 10000, seed = 42))

# n = 32
df0.n32 <- as.data.frame(freq.bayes(sample.size = 32, iterations = 10000, seed = 42))

# n = 64
df0.n64 <- as.data.frame(freq.bayes(sample.size = 64, iterations = 10000, seed = 42))

# n = 100
df0.n100 <- as.data.frame(freq.bayes(sample.size = 100, iterations = 10000, seed = 42))

# n = 300
df0.n300 <- as.data.frame(freq.bayes(sample.size = 300, iterations = 10000, seed = 42))

# n = 500
df0.n500 <- as.data.frame(freq.bayes(sample.size = 500, iterations = 10000, seed = 42))

# n = 2000
df0.n2000 <- as.data.frame(freq.bayes(sample.size = 2000, iterations = 10000, seed = 42))

skrrrahh("bigshaq")
```


## Medium effect (delta = 0.5, difference = 5)
```{r}
# n = 10
df.n10 <- as.data.frame(freq.bayes(sample.size = 10, iterations = 10000, seed = 42, difference = 5))

# n = 32
df.n32 <- as.data.frame(freq.bayes(sample.size = 32, iterations = 10000, seed = 42, difference = 5))

# n = 64
df.n64 <- as.data.frame(freq.bayes(sample.size = 64, iterations = 10000, seed = 42, difference = 5))

# n = 100
df.n100 <- as.data.frame(freq.bayes(sample.size = 100, iterations = 10000, seed = 42, difference = 5))

# n = 300
df.n300 <- as.data.frame(freq.bayes(sample.size = 300, iterations = 10000, seed = 42, difference = 5))

# n = 500
df.n500 <- as.data.frame(freq.bayes(sample.size = 500, iterations = 10000, seed = 42, difference = 5))

# n = 2000
df.n2000 <- as.data.frame(freq.bayes(sample.size = 2000, iterations = 10000, seed = 42, difference = 5))


skrrrahh("bigshaq")
```


## Combine results for null
```{r}
df0 <- rbind(df0.n10, df0.n32, df0.n64, df0.n100, df0.n300, df0.n500, df0.n2000)

# Convert relevant columns to numeric
df0[c(1:15, 28, 29, 33, 34)] <- sapply(df0[c(1:15, 28, 29, 33, 34)], as.numeric)

## Convert BF.evidence, n, and difference to factor
df0$BF.evidence <- as.factor(df0$BF.evidence)
df0$n_num <- df0$n
df0$n <- as.factor(df0$n) %>% fct_relevel(c("10", "32", "64", "300", "100", "500", "2000"))
df0$BF3.decision <- as_factor(df0$BF3.decision) %>% fct_relevel(c("null", "U", "alt"))
df0$BF10.decision <- as_factor(df0$BF10.decision) %>% fct_relevel(c("null", "U", "alt"))
df0$BF30.decision <- as_factor(df0$BF30.decision) %>% fct_relevel(c("null", "U", "alt"))
df0$p.decision <- as_factor(df0$p.decision) %>% fct_relevel(c("null", "alt"))
df0$p.correct <- as.factor(case_when(df0$p <= .05 & df0$difference > 0 & df0$diff_obs  > 0 ~ "correct",
                          df0$p <= .05 & df0$difference < 0 & df0$diff_obs  < 0 ~ "correct",
                          df0$p > .05 & df0$difference == 0 ~ "correct",
                          TRUE ~ "incorrect"))
df0$HDI.correct <- as.factor(case_when(df0$HDI.decision == "null" & df0$difference == 0 ~ "correct",
                                       df0$HDI.decision == "alt" & df0$difference > 0 & df0$diff_obs > 0 ~ "correct",
                                       df0$HDI.decision == "alt" & df0$difference < 0 & df0$diff_obs < 0 ~ "correct",
                                       TRUE ~ "incorrect"))
df0$BF1.correct <- as.factor(case_when(df0$BF1.decision == "null" & df0$difference == 0 ~ "correct",
                                       df0$BF1.decision == "alt" & df0$difference > 0 & df0$diff_obs > 0 ~ "correct",
                                       df0$BF1.decision == "alt" & df0$difference < 0 & df0$diff_obs < 0 ~ "correct",
                                       TRUE ~ "incorrect"))
df0$difference <- as.factor(df0$difference) 
df0$BF.3.cor <- as_factor(df0$BF.3.cor) %>% fct_relevel(c("incorrect", "correct"))
df0$BF.10.cor <- as_factor(df0$BF.10.cor) %>% fct_relevel(c("incorrect", "correct"))
df0$BF.30.cor <- as_factor(df0$BF.30.cor) %>% fct_relevel(c("incorrect", "correct"))
df0$BF.3.ninc <- as_factor(df0$BF.3.ninc) %>% fct_relevel(c("incorrect", "correct"))
df0$BF.10.ninc <- as_factor(df0$BF.10.ninc) %>% fct_relevel(c("incorrect", "correct"))
df0$BF.30.ninc <- as_factor(df0$BF.30.ninc) %>% fct_relevel(c("incorrect", "correct"))
df0$BF1.decision <- as_factor(df0$BF1.decision) %>% fct_relevel(c("null", "alt"))
df0$HDI.decision <- as_factor(df0$HDI.decision)  %>% fct_relevel(c("null", "alt"))
df0$HDI.est.correct <- as_factor(df0$HDI.est.correct) %>% fct_relevel(c("incorrect", "correct"))
df0$CI.est.correct <- as_factor(df0$CI.est.correct) %>% fct_relevel(c("incorrect", "correct"))
```

## Combine results for delta = .5
```{r}
df <- rbind(df.n10, df.n32, df.n64, df.n100, df.n300, df.n500, df.n2000)

# Convert relevant columns to numeric
df[c(1:15, 28, 29, 33, 34)] <- sapply(df[c(1:15, 28, 29, 33, 34)], as.numeric)

## Convert BF.evidence, n, and difference to factor
df$BF.evidence <- as.factor(df$BF.evidence)
df$n_num <- df$n
df$n <- as.factor(df$n) %>% fct_relevel(c("10", "32", "64", "300", "100", "500", "2000"))
df$BF3.decision <- as.factor(df$BF3.decision) %>% fct_relevel(c("null", "U", "alt"))
df$BF10.decision <- as.factor(df$BF10.decision) %>% fct_relevel(c("null", "U", "alt"))
df$BF30.decision <- as.factor(df$BF30.decision) %>% fct_relevel(c("null", "U", "alt"))
df$p.decision <- as.factor(df$p.decision) %>% fct_relevel(c("null", "alt"))
df$p.correct <- as.factor(case_when(df$p <= .05 & df$difference > 0 & df$diff_obs  > 0 ~ "correct",
                          df$p <= .05 & df$difference < 0 & df$diff_obs  < 0 ~ "correct",
                          df$p > .05 & df$difference == 0 ~ "correct",
                          TRUE ~ "incorrect"))
df$HDI.correct <- as.factor(case_when(df$HDI.decision == "null" & df$difference == 0 ~ "correct",
                                       df$HDI.decision == "alt" & df$difference > 0 & df$diff_obs > 0 ~ "correct",
                                       df$HDI.decision == "alt" & df$difference < 0 & df$diff_obs < 0 ~ "correct",
                                       TRUE ~ "incorrect"))
df$BF1.correct <- as.factor(case_when(df$BF1.decision == "null" & df$difference == 0 ~ "correct",
                                       df$BF1.decision == "alt" & df$difference > 0 & df$diff_obs > 0 ~ "correct",
                                       df$BF1.decision == "alt" & df$difference < 0 & df$diff_obs < 0 ~ "correct",
                                       TRUE ~ "incorrect"))
df$difference <- as.factor(df$difference)
df$BF.3.cor <- as_factor(df$BF.3.cor) %>% fct_relevel(c("incorrect", "correct"))
df$BF.10.cor <- as_factor(df$BF.10.cor) %>% fct_relevel(c("incorrect", "correct"))
df$BF.30.cor <- as_factor(df$BF.30.cor) %>% fct_relevel(c("incorrect", "correct"))
df$BF.3.ninc <- as_factor(df$BF.3.ninc) %>% fct_relevel(c("incorrect", "correct"))
df$BF.10.ninc <- as_factor(df$BF.10.ninc) %>% fct_relevel(c("incorrect", "correct"))
df$BF.30.ninc <- as_factor(df$BF.30.ninc) %>% fct_relevel(c("incorrect", "correct"))
df$BF1.decision <- as_factor(df$BF1.decision) %>% fct_relevel(c("null", "alt"))
df$HDI.decision <- as.factor(df$HDI.decision)  %>% fct_relevel(c("null", "alt"))
df$HDI.est.correct <- as.factor(df$HDI.est.correct) %>% fct_relevel(c("incorrect", "correct"))
df$CI.est.correct <- as.factor(df$CI.est.correct) %>% fct_relevel(c("incorrect", "correct"))

```
# Visualizations

## Visualize p-value distributions
```{r}
(p.dis.n10 <- ggplot(df[df$n == 10,], aes(p)) + geom_histogram(bins = 100) + theme_apa() + scale_fill_grey())
(p.dis.n32 <- ggplot(df[df$n == 32,], aes(p)) + geom_histogram(bins = 100) + theme_apa() + scale_fill_grey())
(p.dis.n64 <- ggplot(df[df$n == 64,], aes(p)) + geom_histogram(bins = 100) + theme_apa() + scale_fill_grey())
(p.dis.n100 <- ggplot(df[df$n == 100,], aes(p)) + geom_histogram(bins = 100) + theme_apa() + scale_fill_grey())
(p.dis.n500 <- ggplot(df[df$n == 500,], aes(p)) + geom_histogram(bins = 100) + theme_apa() + scale_fill_grey())

(p.distributions <-
  p.dis.n10/
  p.dis.n32/
  p.dis.n64/
  p.dis.n100/
  p.dis.n500)
```

## Visualize p correct and BF correct for null
```{r}
p.correct.percentage.0 <- df0 %>%
  group_by(n_num, p.correct, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

BF1.correct.percentage.0 <- df0 %>%
  group_by(n_num, BF1.correct, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

HDI.correct.percentage.0 <- df0 %>%
  group_by(n_num, HDI.correct, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

BF3.correct.percentage.0 <- df0 %>%
  group_by(n_num, BF.3.cor, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)
  

BF10.correct.percentage.0 <- df0 %>%
  group_by(n_num, BF.10.cor, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

correct.rows.BF30.cor0 <- data.frame(c(10, 32, 64, 100, 300, 500, 2000),
        c("correct", "correct", "correct", "correct", "correct", "correct", "correct"),
        c(0, 0, 0, 0, 0, 0, 0),
        c(0, 0, 0, 0, 0, 0, 0),
        c(0, 0, 0, 0, 0, 0, 0))

names(correct.rows.BF30.cor0) <- c("n_num", "BF.30.cor", "N", "freq", "pct")

BF30.correct.percentage.0 <- df0 %>%
  group_by(n_num, BF.30.cor, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100) %>%
  as.data.frame() %>%
  plyr::rbind.fill(correct.rows.BF30.cor0)
BF30.correct.percentage.0$BF.30.cor <- as_factor(BF30.correct.percentage.0$BF.30.cor)

ggplot(NULL, aes(x = n_num, y = pct)) + 
  ylim(0, 100) +
  geom_point(data = p.correct.percentage.0[p.correct.percentage.0$p.correct == "correct", ], aes(color = "p < .05")) + 
  geom_line(data = p.correct.percentage.0[p.correct.percentage.0$p.correct == "correct", ], aes(color = "p < .05")) + 
  geom_point(data = HDI.correct.percentage.0[HDI.correct.percentage.0$HDI.correct == "correct", ], aes(color = "HDI")) +
  geom_line(data = HDI.correct.percentage.0[HDI.correct.percentage.0$HDI.correct == "correct", ], aes(color = "HDI")) +
  geom_point(data = BF1.correct.percentage.0[BF1.correct.percentage.0$BF1.correct == "correct", ], aes(color = "BF > 1")) + 
  geom_line(data = BF1.correct.percentage.0[BF1.correct.percentage.0$BF1.correct == "correct", ], aes(color = "BF > 1")) + 
  geom_point(data = BF3.correct.percentage.0[BF3.correct.percentage.0$BF.3.cor == "correct", ], aes(color = "BF > 3")) +
  geom_line(data = BF3.correct.percentage.0[BF3.correct.percentage.0$BF.3.cor == "correct", ], aes(color = "BF > 3")) +
  geom_point(data = BF10.correct.percentage.0[BF10.correct.percentage.0$BF.10.cor == "correct", ], aes(color = "BF > 10")) +
  geom_line(data = BF10.correct.percentage.0[BF10.correct.percentage.0$BF.10.cor == "correct", ], aes(color = "BF > 10")) +
  geom_point(data = BF30.correct.percentage.0[BF30.correct.percentage.0$BF.30.cor == "correct", ], aes(color = "BF > 30")) +
  geom_line(data = BF30.correct.percentage.0[BF30.correct.percentage.0$BF.30.cor == "correct", ], aes(color = "BF > 30")) +
 scale_colour_manual("", 
                      breaks = c("p < .05", "HDI", "BF > 1", "BF > 3", "BF > 10", "BF > 30"),
                      values = c("black", "blue", "pink", "orange", "red", "purple")) +
  theme_apa() +
  scale_x_continuous(name = "Sample Size", breaks = c(10, 32, 64, 100, 300, 500, 2000)) +
  ylab("Percentage of Correct Samples") +
  ggtitle("Times Chosen for the Null when it is True")
```

## Visualize incorrect p and BF decisions for null
```{r}
BF3.incorrect.percentage.0 <- df0 %>%
  group_by(n_num, BF.3.ninc, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)
  
BF10.incorrect.percentage.0 <- df0 %>%
group_by(n_num, BF.10.ninc, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

BF30.incorrect.percentage.0 <- df0 %>%
  group_by(n_num, BF.30.ninc, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

ggplot(NULL, aes(x = n_num, y = pct)) + 
  ylim(0, 15) +
  geom_point(data = p.correct.percentage.0[p.correct.percentage.0$p.correct == "incorrect", ], aes(color = "p < .05")) + 
  geom_line(data = p.correct.percentage.0[p.correct.percentage.0$p.correct == "incorrect", ], aes(color = "p < .05")) + 
  geom_point(data = HDI.correct.percentage.0[HDI.correct.percentage.0$HDI.correct == "incorrect", ], aes(color = "HDI")) +
  geom_line(data = HDI.correct.percentage.0[HDI.correct.percentage.0$HDI.correct == "incorrect", ], aes(color = "HDI")) +
  geom_point(data = BF1.correct.percentage.0[BF1.correct.percentage.0$BF1.correct == "incorrect", ], aes(color = "BF > 1")) + 
  geom_line(data = BF1.correct.percentage.0[BF1.correct.percentage.0$BF1.correct == "incorrect", ], aes(color = "BF > 1")) + 
  geom_point(data = BF3.incorrect.percentage.0[BF3.incorrect.percentage.0$BF.3.ninc == "incorrect", ], aes(color = "BF > 3")) +
  geom_line(data = BF3.incorrect.percentage.0[BF3.incorrect.percentage.0$BF.3.ninc == "incorrect", ], aes(color = "BF > 3")) +
  geom_point(data = BF10.incorrect.percentage.0[BF10.incorrect.percentage.0$BF.10.ninc == "incorrect", ], aes(color = "BF > 10")) +
  geom_line(data = BF10.incorrect.percentage.0[BF10.incorrect.percentage.0$BF.10.ninc == "incorrect", ], aes(color = "BF > 10")) +
  geom_point(data = BF30.incorrect.percentage.0[BF30.incorrect.percentage.0$BF.30.ninc == "incorrect", ], aes(color = "BF > 30")) +
  geom_line(data = BF30.incorrect.percentage.0[BF30.incorrect.percentage.0$BF.30.ninc == "incorrect", ], aes(color = "BF > 30")) +
  scale_colour_manual("", 
                      breaks = c("p < .05", "HDI", "BF > 1", "BF > 3", "BF > 10", "BF > 30"),
                      values = c("black", "blue", "pink", "orange", "red", "purple")) +
  theme_apa() +
  scale_x_continuous(name = "Sample Size", breaks = c(10, 32, 64, 100, 300, 500, 2000)) +
  ylab("Percentage of Incorrect Samples") +
  ggtitle("Times Chosen for the Alternative when the Null is True")
```

## Visualize p correct and BF correct for alt
```{r}
p.correct.percentage <- df %>%
  group_by(n_num, p.correct, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

BF1.correct.percentage <- df %>%
  group_by(n_num, BF1.correct, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

HDI.correct.percentage <- df %>%
  group_by(n_num, HDI.correct, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

BF3.correct.percentage <- df %>%
  group_by(n_num, BF.3.cor, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

BF10.correct.percentage <- df %>%
group_by(n_num, BF.10.cor, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

BF30.correct.percentage <- df %>%
  group_by(n_num, BF.30.cor, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

ggplot(NULL, aes(x = n_num, y = pct)) + 
  ylim(0, 100) +
  geom_point(data = p.correct.percentage[p.correct.percentage$p.correct == "correct", ], aes(color = "p < .05")) + 
  geom_line(data = p.correct.percentage[p.correct.percentage$p.correct == "correct", ], aes(color = "p < .05")) + 
  geom_point(data = HDI.correct.percentage[HDI.correct.percentage$HDI.correct == "correct", ], aes(color = "HDI")) +
  geom_line(data = HDI.correct.percentage[HDI.correct.percentage$HDI.correct == "correct", ], aes(color = "HDI")) +
  geom_point(data = BF1.correct.percentage[BF1.correct.percentage$BF1.correct == "correct", ], aes(color = "BF > 1")) + 
  geom_line(data = BF1.correct.percentage[BF1.correct.percentage$BF1.correct == "correct", ], aes(color = "BF > 1")) +
  geom_point(data = BF3.correct.percentage[BF3.correct.percentage$BF.3.cor == "correct", ], aes(color = "BF > 3")) +
  geom_line(data = BF3.correct.percentage[BF3.correct.percentage$BF.3.cor == "correct", ], aes(color = "BF > 3")) +
  geom_point(data = BF10.correct.percentage[BF10.correct.percentage$BF.10.cor == "correct", ], aes(color = "BF > 10")) +
  geom_line(data = BF10.correct.percentage[BF10.correct.percentage$BF.10.cor == "correct", ], aes(color = "BF > 10")) +
  geom_point(data = BF30.correct.percentage[BF30.correct.percentage$BF.30.cor == "correct", ], aes(color = "BF > 30")) +
  geom_line(data = BF30.correct.percentage[BF30.correct.percentage$BF.30.cor == "correct", ], aes(color = "BF > 30")) +
  scale_colour_manual("", 
                      breaks = c("p < .05", "HDI", "BF > 1", "BF > 3", "BF > 10", "BF > 30"),
                      values = c("black", "blue", "pink", "orange", "red", "purple")) +
  theme_apa() +
  scale_x_continuous(name = "Sample Size", breaks = c(10, 32, 64, 100, 300, 500, 2000)) +
  ylab("Percentage of Correct Samples") +
  ggtitle("Times Chosen for the Alternative when it is True")
```

## Visualize incorrect p and BF decisions for alt
```{r}
incorrect.rows.BF10.incor <- data.frame(c(10, 32, 64, 100, 300, 500, 2000),
        c("incorrect", "incorrect", "incorrect", "incorrect", "incorrect", "incorrect", "inorrect"),
        c(0, 0, 0, 0, 0, 0, 0),
        c(0, 0, 0, 0, 0, 0, 0),
        c(0, 0, 0, 0, 0, 0, 0))

names(incorrect.rows.BF10.incor) <- c("n_num", "BF.10.ninc", "N", "freq", "pct")

incorrect.rows.BF30.incor <- data.frame(c(10, 32, 64, 100, 300, 500, 2000),
        c("incorrect", "incorrect", "incorrect", "incorrect", "incorrect", "incorrect", "inorrect"),
        c(0, 0, 0, 0, 0, 0, 0),
        c(0, 0, 0, 0, 0, 0, 0),
        c(0, 0, 0, 0, 0, 0, 0))

names(incorrect.rows.BF30.incor) <- c("n_num", "BF.30.ninc", "N", "freq", "pct")

BF3.incorrect.percentage <- df %>%
  group_by(n_num, BF.3.ninc, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)

BF10.incorrect.percentage <- df %>%
group_by(n_num, BF.10.ninc, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100)  %>%
  as.data.frame() %>%
  plyr::rbind.fill(incorrect.rows.BF10.incor)

BF10.incorrect.percentage$BF.10.ninc <- as_factor(BF10.incorrect.percentage$BF.10.ninc)

BF30.incorrect.percentage <- df %>%
  group_by(n_num, BF.30.ninc, .drop = FALSE) %>%
  summarize(N = n()) %>%
  mutate(freq = N/sum(N),
         pct = freq*100) %>%
  as.data.frame() %>%
  plyr::rbind.fill(incorrect.rows.BF30.incor)
BF30.incorrect.percentage$BF.30.ninc <- as_factor(BF30.incorrect.percentage$BF.30.ninc)

ggplot(NULL, aes(x = n_num, y = pct)) + 
  ylim(0, 100) +
  geom_point(data = p.correct.percentage[p.correct.percentage$p.correct == "incorrect", ], aes(color = "p < .05")) + 
  geom_line(data = p.correct.percentage[p.correct.percentage$p.correct == "incorrect", ], aes(color = "p < .05")) + 
  geom_point(data = HDI.correct.percentage[HDI.correct.percentage$HDI.correct == "incorrect", ], aes(color = "HDI")) +
  geom_line(data = HDI.correct.percentage[HDI.correct.percentage$HDI.correct == "incorrect", ], aes(color = "HDI")) +
  geom_point(data = BF1.correct.percentage[BF1.correct.percentage$BF1.correct == "incorrect", ], aes(color = "BF > 1")) + 
  geom_line(data = BF1.correct.percentage[BF1.correct.percentage$BF1.correct == "incorrect", ], aes(color = "BF > 1")) + 
  geom_point(data = BF3.incorrect.percentage[BF3.incorrect.percentage$BF.3.ninc == "incorrect", ], aes(color = "BF > 3")) +
  geom_line(data = BF3.incorrect.percentage[BF3.incorrect.percentage$BF.3.ninc == "incorrect", ], aes(color = "BF > 3")) +
  geom_point(data = BF10.incorrect.percentage[BF10.incorrect.percentage$BF.10.ninc == "incorrect", ], aes(color = "BF > 10")) +
  geom_line(data = BF10.incorrect.percentage[BF10.incorrect.percentage$BF.10.ninc == "incorrect", ], aes(color = "BF > 10")) +
  geom_point(data = BF30.incorrect.percentage[BF30.incorrect.percentage$BF.30.ninc == "incorrect", ], aes(color = "BF > 30")) +
  geom_line(data = BF30.incorrect.percentage[BF30.incorrect.percentage$BF.30.ninc == "incorrect", ], aes(color = "BF > 30")) +
  scale_colour_manual("", 
                      breaks = c("p < .05", "HDI", "BF > 1", "BF > 3", "BF > 10", "BF > 30"),
                      values = c("black", "blue", "pink", "orange", "red", "purple")) +
  theme_apa() +
  scale_x_continuous(name = "Sample Size", breaks = c(10, 32, 64, 100, 300, 500, 2000)) +
  ylab("Percentage of Incorrect Samples") +
  ggtitle("Times Chosen for the Null when the Alternative is True")
```

## Examine precision of confidence interval and HDI
```{r}
width <- df %>%
  group_by(n) %>%
  select("ci.width", "hdi.width") %>%
  skim()
```
Create density plots for null
```{r}
d0.10 = data.frame(x = c(df0[df0$n == 10,]$ci.width, df0[df0$n == 10,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df0[df0$n == 10,]$ci.width), length(df0[df0$n == 10,]$hdi.width))))

width.plot0.10 <- ggplot(d0.10) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

d0.32 = data.frame(x = c(df0[df0$n == 32,]$ci.width, df0[df0$n == 32,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df0[df0$n == 32,]$ci.width), length(df0[df0$n == 32,]$hdi.width))))

width.plot0.32 <- ggplot(d0.32) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

d0.64 = data.frame(x = c(df0[df0$n == 64,]$ci.width, df0[df0$n == 64,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df0[df0$n == 64,]$ci.width), length(df0[df0$n == 64,]$hdi.width))))

width.plot0.64 <- ggplot(d0.64) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

d0.100 = data.frame(x = c(df0[df0$n == 100,]$ci.width, df0[df0$n == 100,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df0[df0$n == 100,]$ci.width), length(df0[df0$n == 100,]$hdi.width))))

width.plot0.100 <- ggplot(d0.100) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

d0.500 = data.frame(x = c(df0[df0$n == 500,]$ci.width, df0[df0$n == 500,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df0[df0$n == 500,]$ci.width), length(df0[df0$n == 500,]$hdi.width))))

width.plot0.500 <- ggplot(d.500) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

(plot0 <- width.plot0.10/
width.plot0.32/
width.plot0.64/
width.plot0.100/
width.plot0.500)
```
Create density plots for delta = 0.5
```{r}
d.10 = data.frame(x = c(df[df$n == 10,]$ci.width, df[df$n == 10,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df[df$n == 10,]$ci.width), length(df[df$n == 10,]$hdi.width))))

width.plot.10 <- ggplot(d.10) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

d.32 = data.frame(x = c(df[df$n == 32,]$ci.width, df[df$n == 32,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df[df$n == 32,]$ci.width), length(df[df$n == 32,]$hdi.width))))

width.plot.32 <- ggplot(d.32) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

d.64 = data.frame(x = c(df[df$n == 64,]$ci.width, df[df$n == 64,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df[df$n == 64,]$ci.width), length(df[df$n == 64,]$hdi.width))))

width.plot.64 <- ggplot(d.64) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

d.100 = data.frame(x = c(df[df$n == 100,]$ci.width, df[df$n == 100,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df[df$n == 100,]$ci.width), length(df[df$n == 100,]$hdi.width))))

width.plot.100 <- ggplot(d.100) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

d.500 = data.frame(x = c(df[df$n == 500,]$ci.width, df[df$n == 500,]$hdi.width), 
               type=rep(c("CI Width", "HDI Width"), c(length(df[df$n == 500,]$ci.width), length(df[df$n == 500,]$hdi.width))))

width.plot.500 <- ggplot(d.500) + geom_density(aes(x=x, fill=type), alpha = 0.5) + theme_apa() + scale_fill_grey()

(plot <- width.plot.10/
width.plot.32/
width.plot.64/
width.plot.100/
width.plot.500)
```
^ Still have to fix the axes so they can be compared visually

## Show corresponding conclusions for null
```{r}
# Set alpha and size -----------------------------------------------------------
a <- 0.1
s <- 0.1

# For p values and Bayes factor cutoffs-----------------------------------------
(bf3.p.plot.0 <- ggplot(df0, aes(x = BF3.decision, y = p.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))
(bf10.p.plot.0 <- ggplot(df0, aes(x = BF10.decision, y = p.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))
(bf30.p.plot.0 <- ggplot(df0, aes(x = BF30.decision, y = p.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))

(bf.p.plot.0 <- 
  bf3.p.plot.0/
  bf10.p.plot.0/
  bf30.p.plot.0)

# For HDI and BF cutoffs --------------------------------------------------------

(bf3.hdi.plot.0 <- ggplot(df0, aes(x = BF3.decision, y = HDI.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))
(bf10.hdi.plot.0 <- ggplot(df0, aes(x = BF10.decision, y = HDI.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))
(bf30.hdi.plot.0 <- ggplot(df0, aes(x = BF30.decision, y = HDI.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))

(bf.hdi.plot.0 <- 
  bf3.hdi.plot.0/
  bf10.hdi.plot.0/
  bf30.hdi.plot.0)

# For p values and HDI ---------------------------------------------------------
(hdi.p.plot.0 <- ggplot(df0, aes(x = HDI.decision, y = p.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))

# For CI and HDI estimation ----------------------------------------------------
(hdi.ci.plot.0 <- ggplot(df0, aes(x = HDI.est.correct, y = CI.est.correct)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))
```

## Show corresponding conclusions for d = 0.5
```{r}
# Set alpha and size -----------------------------------------------------------
a <- 0.1
s <- 0.1

# For p values and Bayes factor cutoffs-----------------------------------------
(bf3.p.plot <- ggplot(df, aes(x = BF3.decision, y = p.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))
(bf10.p.plot <- ggplot(df, aes(x = BF10.decision, y = p.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))
(bf30.p.plot <- ggplot(df, aes(x = BF30.decision, y = p.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))

(bf.p.plot <- 
  bf3.p.plot/
  bf10.p.plot/
  bf30.p.plot)

# For HDI and BF cutoffs --------------------------------------------------------

(bf3.hdi.plot <- ggplot(df, aes(x = BF3.decision, y = HDI.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))
(bf10.hdi.plot <- ggplot(df, aes(x = BF10.decision, y = HDI.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))
(bf30.hdi.plot <- ggplot(df, aes(x = BF30.decision, y = HDI.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))

(bf.hdi.plot <- 
  bf3.hdi.plot/
  bf10.hdi.plot/
  bf30.hdi.plot)

# For p values and HDI ---------------------------------------------------------
(hdi.p.plot <- ggplot(df, aes(x = HDI.decision, y = p.decision)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))

# For CI and HDI estimation ----------------------------------------------------
(hdi.ci.plot <- ggplot(df, aes(x = HDI.est.correct, y = CI.est.correct)) + geom_jitter(alpha = a, size = s) + theme_apa() + scale_fill_grey() + facet_grid(cols = vars(n)))

skrrrahh("snoop")
```

## Bar plots for corresponding conclusions at null
```{r}
ggplot(data = df0,
       aes(x = BF1.decision, fill = HDI.decision)) + 
  facet_grid(cols = vars(n)) +
  geom_bar(aes(y = (..count..)/sum(..count..)*5)) +
  ylab(label = "Percentage") +
  xlab(label = "Decision for Decision Rule BF > 1") +
  theme_apa()

```
## Bar plots for corresponding conclusions for alternative
```{r}
ggplot(data = df,
       aes(x = BF1.decision, fill = HDI.decision)) +
  geom_bar(aes(y = (..count..)/sum(..count..))) +
  ylab(label = "Percentage") +
  xlab(label = "Decision for Decision Rule BF > 1") +
  theme_apa()
```

